---
title: "Python code chunks in R Markdown"
date: 2018-02-22
---

# Python

## A normal R code chunk

```{r}
x = 42
print(x)
```

## Modify an R variable

In the following chunk, the value of `x` on the right hand side
is `r x`, which was defined in the previous chunk.

```{r}
x = x + 12
print(x)
```

## A Python chunk

This works fine and as expected. 

```{python}
print('Python version = ', sys.version)

x = 42 * 2
print(x) 
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18 
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y = 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```

## Python graphics

You can draw plots using the **matplotlib** package in Python.

```{python, echo=TRUE}
import matplotlib.pyplot as plt
plt.plot([0, 2, 1, 4])
plt.show()
```

and adding a figure caption

````markdown
`r ''````{python testfig1, echo=FALSE, out.width='33%', fig.align='center', fig.cap = 'A figure from Python code'}
plt.plot([0, 2, 1, 4])
plt.show()
```
````

```{python testfig1, echo=FALSE, out.width='33%', fig.align='center', fig.cap = 'A figure from Python code'}
plt.plot([0, 2, 1, 4])
plt.show()
```

Note this last chunk fails when knitr version is knitr_1.28, but works with knitr_1.26.

Using an R chunk to insert a figure with caption:

````markdown
`r ''````{r testfig2, echo=FALSE, out.width='33%', fig.align='center', fig.cap='A figure from a PDF file.'}
knitr::include_graphics('img/testfig1.pdf')
```
````

```{r testfig2, echo=FALSE, out.width='33%', fig.align='center', fig.cap='A figure from a PDF file.'}
knitr::include_graphics('img/testfig1.pdf')
```

Can cite both Figs. \@ref(fig:testfig1) and \@ref(fig:testfig2).

## Using the mib plotting untility

```{python plotP1, echo = TRUE, out.width='66%', fig.align='center', fig.cap ='A plot using mib/utils.py'}
x = np.arange(-10,10,.01)
t = [0.1,0.3,1,3,10]
y = [np.exp(-x**2/(4*ti))/np.sqrt(4*np.pi*ti) for ti in t]
plot (x,y,fmts=['g-', 'm--', 'b-.', 'r:', 'k-'], linewidth=1,
    xlabel='Distance',ylabel='Concentration',yzero=True,
    legend=['t = 0.1','0.3','1','3','10'],xticks=[-10,-5,-1,0,1,5,10])
save_img('plotP1.pdf')
plt.show()
```

See Figure \@ref(fig:plotP1).
