---
title: "Python code chunks in R Markdown"
date: 2018-02-22
---

# Python

## A normal R code chunk

```{r}
x = 42
print(x)
```

## Modify an R variable

In the following chunk, the value of `x` on the right hand side
is `r x`, which was defined in the previous chunk.

```{r}
x = x + 12
print(x)
```

## A Python chunk

This works fine and as expected. 

```{python}
print('Python version = ', sys.version)

x = 42 * 2
print(x) 
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18 
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y = 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```

## Python graphics

You can draw plots using the **matplotlib** package in Python.

```{python, echo='TRUE'}
import matplotlib.pyplot as plt
plt.plot([0, 2, 1, 4])
plt.show()
```

But doing the same with a figure caption fails to build on Travis CI (as of 3/4/2020):

````markdown
`r ''````{python testfig1, echo='FALSE', out.width='33%', fig.align='center', fig.cap = 'A figure from Python code'}
plt.plot([0, 2, 1, 4])
plt.show()
```
````

```{python testfig1, echo='FALSE', out.width='33%', fig.align='center', fig.cap = 'A figure from Python code'}
plt.plot([0, 2, 1, 4])
plt.show()
```

Using an R chunk to insert a figure with caption works fine:

````markdown
`r ''````{r testfig2, echo='FALSE', out.width='33%', fig.align='center', fig.cap='A figure from a PDF file.'}
knitr::include_graphics('img/testfig1.pdf')
```
````

```{r testfig2, echo='FALSE', out.width='33%', fig.align='center', fig.cap='A figure from a PDF file.'}
knitr::include_graphics('img/testfig1.pdf')
```

