--- 
title: "A Test of integrating bookdown with Travis CI"
author: "Markus Meister"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: markusmeister/travis-test
description: "This is a test of various bookdown functions implemented on Travis CI. The content is largely based on Yihui Xie's bookdown projects, see https://bookdown.org/yihui/bookdown/github.html and https://github.com/rstudio/bookdown-demo."
---

# Prerequisites

<!-- ```{r} -->
<!-- install.packages('tinytex') -->
<!-- tinytex::install_tinytex() -->
<!-- ``` -->

```{r}
projdir = rprojroot::find_rstudio_root_file() # project directory

include_svg = function(path) { # used to convert svg to pdf
  if (knitr::is_latex_output()) {
    output = xfun::with_ext(path, 'pdf')
    # you can compare the timestamp of pdf against svg to avoid conversion if necessary
    system2('rsvg-convert', c('-f', 'pdf', '-a', '-o', shQuote(c(output, path))))
  } else {
    output = path
  }
  knitr::include_graphics(output)
}
```

```{r}
# connect to python
library(reticulate)
matplotlib <- import("matplotlib")
matplotlib$use("Agg", force = TRUE) # backend that doesn't expect a display
```

```{python}
import numpy as np
import os
import sys
import matplotlib
matplotlib.rcParams['text.usetex'] = True # use Latex to draw all text
matplotlib.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
import matplotlib.pyplot as plt
curdir = os.getcwd()
os.chdir(r.projdir)
from mib.utils import plot, save_img # plotting routines
os.chdir(curdir)
```

<!--chapter:end:index.Rmd-->

# Equations

## Inline equations
...are enclosed by simple `$  $`, like this:

```
$\tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'\,$
```

which produces this output: $\tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'\,$.

## Display equations
...without numbers can be enclosed by double `$$  $$`, like this: 

```
$$\tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'\,.$$
```

which produces

$$\tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'\,.$$

## Equation labels
To label an equation with `name` use the format `(\#eq:name)`. 
To cite that equation use the format `\@ref(eq:name)`

The equation label has to appear after the body of the equation code, like this:

```latex
\begin{equation} 
  \tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'
  (\#eq:binom)
\end{equation} 
```

\begin{equation}
  \tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'
  (\#eq:binom)
\end{equation}

```latex
\begin{equation}
f\left(k\right)=\binom{n}{k}p^k\left(1-p\right)^{n-k} (\#eq:binom2)
\end{equation}
```

\begin{equation}
f\left(k\right)=\binom{n}{k}p^k\left(1-p\right)^{n-k} (\#eq:binom2)
\end{equation}

Then you can cite the equation, like this: \@ref(eq:binom).

Changed this 5:11PM.

## Equation numbering
There is some weirdness about how equation numbering is handled in the PDF versus the HTML versions of the book. 

In the PDF output equations are numbered by default. Every line of an equation will get numbered except if it

1. is inside `$$ $$`.
2. has `\notag` at the end of line, before the `\\`.
3. is in an `{equation*}` or `{align*}` environment where there are no labels
4. is in a `{split}` environment with a single label

But in the HTML output an equation is unnumbered by default, except if it contains an explicit equation label. For more details see [here](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html). 

So, to make sure we get the same numbering in PDF and HTML we should do this:

**An unnumbered display equation** should be enclosed with `$$ $$` or in environments `{equation*}` or `{align*}`.

**A numbered display equation** should include a single label.

Here are some examples:

This equation will get a number in PDF but not in HTML, **which is a mistake!**

\begin{equation} 
  \tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'
\end{equation} 

This gets no number in PDF or HTML:

\begin{equation*} 
  \tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'
\end{equation*} 

And this gets a number in both PDF and HTML:

\begin{equation} 
  \tilde h(\omega) = \int_{-\infty}^{\infty}\,e^{i\omega t'} h(t') \, dt'
  (\#eq:transfu)
\end{equation} 

## Multi-line equation with multiple labels
Here is a long equation stretching over several lines, first with a single number

\begin{equation} 
\begin{split}
\mathrm{Var}(\hat{\beta}) & =\mathrm{Var}((X'X)^{-1}X'y)\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)((X'X)^{-1}X')'\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)X(X'X)^{-1}\\
 & =(X'X)^{-1}X'\sigma^{2}IX(X'X)^{-1}\\
 & =(X'X)^{-1}\sigma^{2}
\end{split}
(\#eq:var-beta1)
\end{equation} 

...then with multiple numbers

\begin{align}
\mathrm{Var}(\hat{\beta}) & =\mathrm{Var}((X'X)^{-1}X'y) \nonumber \\
 & =(X'X)^{-1}X'\mathrm{Var}(y)((X'X)^{-1}X')'(\#eq:var-a)\\ 
 & =(X'X)^{-1}X'\mathrm{Var}(y)X(X'X)^{-1}(\#eq:var-b)\\ 
 & =(X'X)^{-1}X'\sigma^{2}IX(X'X)^{-1}(\#eq:var-c)\\ 
 & =(X'X)^{-1}\sigma^{2} (\#eq:var-d)
\end{align}


I wrote some grep routines that produce automatic equation labels, for example in the study guide which contains several hundred equations. Every one of those has a label, even though we rarely cite those labels.



<!--chapter:end:01-equations.Rmd-->

---
title: "Python code chunks in R Markdown"
date: 2018-02-22
---

# Python

## A normal R code chunk

```{r}
x = 42
print(x)
```

## Modify an R variable

In the following chunk, the value of `x` on the right hand side
is `r x`, which was defined in the previous chunk.

```{r}
x = x + 12
print(x)
```

## A Python chunk

This works fine and as expected. 

```{python}
print('Python version = ', sys.version)

x = 42 * 2
print(x) 
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18 
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y = 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```

## Python graphics

You can draw plots using the **matplotlib** package in Python.

```{python, echo=TRUE}
import matplotlib.pyplot as plt
plt.plot([0, 2, 1, 4])
plt.show()
```

and adding a figure caption

````markdown
`r ''````{python testfig1, echo=FALSE, out.width='33%', fig.align='center', fig.cap = 'A figure from Python code'}
plt.plot([0, 2, 1, 4])
plt.show()
```
````

```{python testfig1, echo=FALSE, out.width='33%', fig.align='center', fig.cap = 'A figure from Python code'}
plt.plot([0, 2, 1, 4])
plt.show()
```

Note this last chunk fails when knitr version is knitr_1.28, but works with knitr_1.26.

Using an R chunk to insert a figure with caption:

````markdown
`r ''````{r testfig2, echo=FALSE, out.width='33%', fig.align='center', fig.cap='A figure from a PDF file.'}
knitr::include_graphics('img/testfig1.pdf')
```
````

```{r testfig2, echo=FALSE, out.width='33%', fig.align='center', fig.cap='A figure from a PDF file.'}
knitr::include_graphics('img/testfig1.pdf')
```

Can cite both Figs. \@ref(fig:testfig1) and \@ref(fig:testfig2).

## Using the mib plotting untility

```{python plotP1, echo = TRUE, out.width='66%', fig.align='center', fig.cap ='A plot using mib/utils.py'}
x = np.arange(-10,10,.01)
t = [0.1,0.3,1,3,10]
y = [np.exp(-x**2/(4*ti))/np.sqrt(4*np.pi*ti) for ti in t]
plot (x,y,fmts=['g-', 'm--', 'b-.', 'r:', 'k-'], linewidth=1,
    xlabel='Distance',ylabel='Concentration',yzero=True,
    legend=['t = 0.1','0.3','1','3','10'],xticks=[-10,-5,-1,0,1,5,10])
save_img('plotP1.pdf')
plt.show()
```

See Figure \@ref(fig:plotP1).

<!--chapter:end:02-python.Rmd-->

